---
title: "An Interactive Application for Comparing College Majors"
author: "Felix Gerlsbeck"
date: "2/4/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Who is this app for?

- Students today face a difficult choice when deciding on their college major. Besides personal interest, the expected income and unemployment rate for their chosen field are important in determining their choice.

- So far it has been difficult to get all the relevant data in one place.

- A graphical representation to see at a glance where their chosen major falls compared to alternatives has so far been missing.

## The College Major Selection App: Data and Method

- This app uses recent data from Fivethirtyeight.com on the median income and the current unemployment rate for different college majors.

- For 16 different categories of college major, it calculates the average unemployment rate and median income.

- Students can easily choose a major category on the left of the app, and see at a glance where their choice falls within the other options they have.

- The app also gives the exact numbers for the median income and unemployment rate for the chosen category.

## Included College Major Categories
The following categories can be selected in the app:
```{r majors, echo = FALSE, message = FALSE, comment = ""}
library(fivethirtyeight)
library(dplyr)
data(college_all_ages)
names <- unique(college_all_ages$major_category)
names
```

## Choice of College Major is Important
The choice of college major is of great importance for students, as the range both of the unemployment rate and the median income is great, as the following figure shows.
```{r pressure, echo = FALSE}
plot(college_all_ages$median, college_all_ages$unemployment_rate, pch = 16, xlab="Median income of college major", ylab="Unemployment rate of college major")
```

